---
output:
  html_document: default
---


# Hydrostatic pressure and temperature affect the tolerance of the free-living marine nematode <em>Halomonhystera disjuncta</em> to acute copper exposure


###                    Mevenkamp, L., Brown, A., Hauton, C., Kordas, A., Thatje, S., & Vanreusel, A. (2017). 192, 178-183.

####                    The dose response curves were calculated using the log-normal function (LN.2) model from the R statistical package <em>drc</em>. These are the results published in the manuscript:

```{r setup, include= FALSE, tidy=TRUE, echo=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
library(car)
library(DT)
library(knitr)
library(ggplot2)
```


```{r include = FALSE, tidy=TRUE, echo=FALSE}
bel.1<-read.csv("www/belowitz-1.csv", row.names = NULL, sep= ",")
names(bel.1)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")

bel.2<-read.csv("www/belowitz-2.csv", row.names = NULL, sep= ",")
names(bel.2)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")

groups = factor(c(bel.1$Condition,bel.2$Condition))
a<-c(bel.1$LC)
b<-c(bel.2$LC)
ab<-c(a,b)
location<-as.factor(c(rep("publication",12),rep("application",12)))
dati.1<-data.frame(ab,location)
```

The Shapiro test results:
```{r tidy=TRUE, echo=FALSE}
shapiro.test(dati.1$ab[location=="publication"])
```
This result indicates 

The Levene test results:
```{r tidy=TRUE, echo=FALSE}
leveneTest(ab~location, data=dati.1, center=mean)
```
This test result indicates 

The anova analysis results between the published data and this application's calculation:
```{r tidy=TRUE, echo=FALSE}
results.lm <- lm(ab~location, data=dati.1)
aov.1<-aov(results.lm)
summary(aov.1)
```
The anova result indicates no significant difference between the published data and the application's calculation


```{r tidy=TRUE, echo=FALSE}
TukeyHSD(aov.1, conf.level=0.95)
```


```{r tidy=TRUE, echo=FALSE}
 bel.12<-read.csv("www/bel12.csv")
bel.12$source<-factor(bel.12$source, levels=c("publication","application"))
ggplot(bel.12, aes(x = factor(A), y = as.numeric(B))) +
  geom_boxplot(aes(x = factor(A), y = as.numeric(B),fill = factor(source))) +
  xlab('Experiment') + ylab(expression(paste("LC"["50"]," (ppm)"))) +
  scale_fill_brewer(palette = 'Set3', name = 'Result Source')  + 
  ggtitle("Comparison between data results") +
  theme(plot.title = element_text(hjust = 0.5))
```

#### Effects of exposure to high concentrations of waterborne Tl on K and Tl concentrations in <i>Chironomus riparius</i> larvae

Belowitz, R., Leonard, E. M., & O'Donnell, M. J. (2014). Effects of exposure to high concentrations of waterborne Tl on K and Tl concentrations in Chironomus riparius larvae. Comparative Biochemistry and Physiology Part C: Toxicology & Pharmacology, 166, 59-64.

This example compares the published data from the cited article to results of this web application using the same raw data. 

##### The Shapiro test using the data from the publication:
```{r,include=TRUE, tidy=TRUE, echo=FALSE}
bel.1<-read.csv("www/belowitz-1.csv", row.names = NULL, sep= ",")# 
names(bel.1)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")

bel.2<-read.csv("www/belowitz-2.csv", row.names = NULL, sep= ",")
names(bel.2)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")

groups = factor(c(bel.1$Condition,bel.2$Condition))
a<-c(bel.1$LC)
b<-c(bel.2$LC)
ab<-c(a,b)
location<-as.factor(c(rep("publication",12),rep("application",12)))
dati.1<-data.frame(ab,location)
shapiro.test(dati.1$ab[location=="publication"])

```
##### The result of the Shapiro test with p values greater than 0.05 assume the both sets of data come from normal distribution.

##### The Levene test results:

##### The Levene's test result of a p-value greater than 0.05 indicates that the variances for both sets of data are not different.

##### The ANOVA analysis:

##### The ANOVA analysis shows that both data sets have statiscally equal means.

##### The Tukey HSD analysis:

##### The Tukey HSD analysis indicates that no significant differences exist between the means of the publication results and the web application  results. 


