
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(car)
library(DT)
```

#### Hydrostatic pressure and temperature affect the tolerance of the free-living marine nematode Halomonhystera disjuncta to acute copper exposure


Mevenkamp, L., Brown, A., Hauton, C., Kordas, A., Thatje, S., & Vanreusel, A. (2017). Hydrostatic pressure and temperature affect the tolerance of the free-living marine nematode Halomonhystera disjuncta to acute copper exposure. Aquatic Toxicology, 192, 178-183.




#### The results reported in the publication:
```{r comment="", tidy=TRUE}
bel.1<-read.csv("belowitz-1.csv", row.names = NULL, sep= ",")
names(bel.1)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")
datatable(bel.1,escape=FALSE,options(DT.options = list(pageLength = 25, language = list(search = 'Filter:')
  )),rownames = FALSE )
```

#### The results for the web application:
```{r comment="", tidy=TRUE}
bel.2<-read.csv("belowitz-2.csv", row.names = NULL, sep= ",")
names(bel.2)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")
datatable(bel.2,escape=FALSE,options(DT.options = list(pageLength = 25, language = list(search = 'Filter:')
  )),rownames = FALSE )
```



```{r comment="", tidy=TRUE}
groups = factor(c(bel.1$Condition,bel.2$Condition))
a<-c(bel.1$LC)
b<-c(bel.2$LC)
ab<-c(a,b)
location<-as.factor(c(rep("publication",12),rep("application",12)))
dati.1<-data.frame(ab,location)
#dati.2<-cbind.data.frame(groups,ab)
```


##### The Shapiro test using the data from the publication:
```{r comment="", tidy=TRUE}
shapiro.test(dati.1$ab[location=="publication"])
```

##### The Shapiro test using the data from the web application:
```{r comment="", tidy=TRUE}
shapiro.test(dati.1$ab[location=="application"])
```
##### The result of the Shapiro test with p values greater than 0.05 assume the both sets of data come from normal distribution.


##### The Levene test results:
```{r comment="", tidy=TRUE}
leveneTest(ab~location, data=dati.1, center=mean)
```
### The Levene's test result of a p-value greater than 0.05 indicates that the variances for both sets of data are not different.

### The ANOVA analysis:
```{r comment="", tidy=TRUE}
results.lm <- lm(ab~location, data=dati.1)
aov.1<-aov(results.lm)
summary(aov.1)
```
### The ANOVA analysis shows that both data sets have statiscally equal means.

### The Tukey HSD analysis:
```{r comment="", tidy=TRUE}
TukeyHSD(aov.1, conf.level=0.95)
```
### The Tukey HSD analysis indicates that no significant differences exist between the means of the publication results and the web application results. 


```{r pressure, echo=FALSE, eval=FALSE}
### Including Plots
plot(ab~groups,data=dati.2)
```

