
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(car)
library(DT)
```

#### Hydrostatic pressure and temperature affect the tolerance of the free-living marine nematode Halomonhystera disjuncta to acute copper exposure


Mevenkamp, L., Brown, A., Hauton, C., Kordas, A., Thatje, S., & Vanreusel, A. (2017). Hydrostatic pressure and temperature affect the tolerance of the free-living marine nematode Halomonhystera disjuncta to acute copper exposure. Aquatic Toxicology, 192, 178-183.


```{r comment= "", tidy=TRUE}
bel.1<-read.csv("belowitz-1.csv", row.names = NULL, sep= ",")
names(bel.1)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")

bel.2<-read.csv("belowitz-2.csv", row.names = NULL, sep= ",")
names(bel.2)<-c("Experiment","LC<sub>50</sub> (&mu;g/L)","lower confidence limit (&mu;g/L)","upper confidence limit (&mu;g/L)")

groups = factor(c(bel.1$Condition,bel.2$Condition))
a<-c(bel.1$LC)
b<-c(bel.2$LC)
ab<-c(a,b)
location<-as.factor(c(rep("publication",12),rep("application",12)))
dati.1<-data.frame(ab,location)
#dati.2<-cbind.data.frame(groups,ab)
```

### The ANOVA analysis:
```{r echo=FALSE}
results.lm <- lm(ab~location, data=dati.1)
aov.1<-aov(results.lm)
s.1<-summary(aov.1)
s.2<-as.data.frame(s.1[[1]])
  datatable(s.2,escape=FALSE,options(DT.options = list(pageLength = 25, language = list(search = 'Filter:'),
                                                            #order = list(list(2, 'asc'), list(1, 'asc')),
                                                            initComplete = JS(
                                                              "function(settings, json) {",
                                                              "$(this.api().table().header()).css({'background-color': '#337ab7', 'color': '#fff'});",
                                                              "}")
  )),rownames = FALSE )
```
### The ANOVA analysis shows that both data sets have statiscally equal means.

### The Tukey HSD analysis:
```{r echo=FALSE}
t.1<-TukeyHSD(aov.1, conf.level=0.95,ordered=TRUE)
t.2<-as.data.frame(t.1$location)
  datatable(t.2,escape=FALSE,options(DT.options = list(pageLength = 25, language = list(search = 'Filter:'),
                                                            #order = list(list(2, 'asc'), list(1, 'asc')),
                                                            initComplete = JS(
                                                              "function(settings, json) {",
                                                              "$(this.api().table().header()).css({'background-color': '#337ab7', 'color': '#fff'});",
                                                              "}")
  )),rownames = FALSE )
```
### The Tukey HSD analysis indicates that no significant differences exist between the means of the publication results and the web application results. 

```{r echo=FALSE}
bel.12$source<-factor(bel.12$source, levels=c("publication","application"))
ggplot(bel.12, aes(x = factor(A), y = as.numeric(B))) +
  geom_boxplot(aes(x = factor(A), y = as.numeric(B),fill = factor(source))) +
  xlab('Experiment') + ylab(expression(paste("LC"["50"]," (ppm)"))) +
  scale_fill_brewer(palette = 'Set3', name = 'Result Source')  + 
  ggtitle("Comparison between data results") +
  theme(plot.title = element_text(hjust = 0.5))
```
